---
title: "Consulting Project Data"
author: "Matt Parker"
date: "2023-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
library(caret)
library(rsample)     # data splitting 
library(dplyr)       # data wrangling
library(rpart)       # performing regression trees
library(rpart.plot)  # plotting regression trees
library(ipred)       # bagging
library(lm.beta)
```

## Demographics

Use histograms, boxplots for demographics

```{r}
data.1 <- na.omit(Data_STAT4893W[, 161:181])
data <- Data_STAT4893W[, 1:85]
```

```{r}
library(gtsummary)

data %>%

  gtsummary::tbl_summary() %>%
  gtsummary::as_kable()

```


## Objective #1: Empirically categorize and/or rank the coping strategies with regard to levels of compassion fatigue

```{r}
## Multiple Linear Regression

m1 <- lm(CFS_SecondaryTrauma_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1)

beta.m1 <- lm.beta(m1)

m2 <- lm(CFS_JobBurnout_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1)

beta.m2 <- lm.beta(m2)

var_names.1 <- names(coef(beta.m1))
coef_vals.1 <- coef(beta.m1)
beta.table.1 <- data.table::data.table("Coping Strategies" = var_names.1, "Betas" = coef_vals.1)
beta.table.1[order(coef_vals.1, decreasing = TRUE)]

var_names.2 <- names(coef(beta.m2))
coef_vals.2 <- coef(beta.m2)
beta.table.2 <- data.table::data.table("Coping Strategies" = var_names.2, "Betas" = coef_vals.2)
beta.table.2[order(coef_vals.2, decreasing = TRUE)]

par(mfrow = c(2, 2))
plot(m2)

par(mfrow = c(2, 2))
plot(m1)
```


```{r}
## Regression Trees

mod.1 <- rpart(CFS_SecondaryTrauma_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1, method = "anova")

rpart.plot(mod.1)

mod.2 <- rpart(CFS_JobBurnout_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1, method = "anova")

rpart.plot(mod.2)
```


```{r}
## Bagging with Caret

ctrl <- trainControl(method = "cv",  number = 10) 

# CV bagged model

bagged_cv.1 <- train(CFS_SecondaryTrauma_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1, method = "treebag", trControl = ctrl, importance = TRUE)

plot(varImp(bagged_cv.1), 15, main = "Importance of Each Covariate in Predicting Secondary Trauma")

bagged_cv.2 <- train(CFS_JobBurnout_ln ~ COPE_Positive + COPE_MentalDis + COPE_Venting + COPE_InstrumentalSup + COPE_Active + COPE_Denial + COPE_Religious + COPE_Humor + COPE_BehavioralDis + COPE_Restraint + COPE_EmotionalSup + COPE_Substance + COPE_Acceptance + COPE_Suppression + COPE_Planning, data = data.1, method = "treebag", trControl = ctrl, importance = TRUE)

plot(varImp(bagged_cv.2), 15, main = "Importance of Each Covariate in Predicting Job Burnout")
```


## Objective #2: Categorizing adaptive/maladaptive coping strategies

Adaptive: Acceptance, Active, Positive, Religious, Restraint, Instrumental Support, and Emotional Support

Maladaptive: Mental Disengagement, Behavioral Disengagement, Denial, Venting, Substance, and Suppression

Mixed: Humor, Planning

```{r}
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering algorithms & visualization
```

```{r}
data.2 <- data.1[, 1:15]
data.adap <- data.2[, c(1, 5, 13, 7, 4, 11, 10)]
data.mal <- data.2[, -c(1, 5, 13, 7, 4, 11, 10)]
```

```{r}
set.seed(1234)

k1 <- kmeans(data.2, centers = 2)
fviz_cluster(k1, data = data.2)
cluster.1 <- data.table::data.table("Variables" = names(data.2), "Cluster #1 Means" = k1$centers[1, ])
cluster.2 <- data.table::data.table("Variables" = names(data.2), "Cluster #2 Means" = k1$centers[2, ])

cluster.1[order(k1$centers[1, ], decreasing = TRUE)]
cluster.2[order(k1$centers[2, ], decreasing = TRUE)]

k1$centers[1, ] - k1$centers[2, ]
```

```{r}
h <- beta.table.2[order(coef_vals.2, decreasing = TRUE)]
View(h[, 2])
```


